SPARQL on the Open, Decentralised Web

### 2016-06-21 dissertation/cache-proxy.tex
Capitalisation; thanks Helen

\chapter{Prefetching SPARQL query cacher}\label{sec:tpfcacheplanning}

@@

\subsection{The Attean framework}\label{sec:attean}

@@

\subsection{SPARQL protocol client}\label{sec:sparqlclient}

@@

\subsection{Linked Data Fragment client}\label{sec:ldfclient}

@@

\subsection{The caching proxy}\label{sec:cacher}

@@

\subsubsection{Analysis and prefetching}\label{sec:analpre}

@@

\subsubsection{Query planner}\label{sec:implqueryplan}

@@

\subsection{Actual evaluation}

@@

\subsection{Planned evaluation}\label{sec:planned}

@@

\subsection{Join rotation and Iterative Dynamic
  Programming}

@@

\subsection{Remedies for performance issues}\label{sec:discussfail}

>>>>

\chapter{Prefetching SPARQL Query Cacher}\label{sec:tpfcacheplanning}

@@

\subsection{The Attean Framework}\label{sec:attean}

@@

\subsection{SPARQL Protocol Client}\label{sec:sparqlclient}

@@

\subsection{Linked Data Fragment Client}\label{sec:ldfclient}

@@

\subsection{The Caching Proxy}\label{sec:cacher}

@@

\subsubsection{Analysis and Prefetching}\label{sec:analpre}

@@

\subsubsection{Query Planner}\label{sec:implqueryplan}

@@

\subsection{Actual Evaluation}

@@

\subsection{Planned Evaluation}\label{sec:planned}

@@

\subsection{Join Rotation and Iterative Dynamic
  Programming}

@@

\subsection{Remedies for Performance Issues}\label{sec:discussfail}

### 2016-06-21 dissertation/papersincontext.tex
Capitalisation; thanks Helen

\section{The papers in context}\label{sec:papersincontext}

@@

\subsection{Read-write hypermedia}\label{sec:conlapis}

@@

\subsection{Pushing complexity down the stack}\label{sec:conpush}

@@

\subsection{Survey of HTTP caching}\label{sec:consanity}

>>>>

\section{The Papers in Context}\label{sec:papersincontext}

@@

\subsection{Read-write Hypermedia}\label{sec:conlapis}

@@

\subsection{Pushing Complexity Down the Stack}\label{sec:conpush}

@@

\subsection{Survey of HTTP Caching}\label{sec:consanity}

### 2016-06-21 dissertation/problems.tex
short section heading
Capitalisation; thanks Helen

\subsection{Performance and stability problems}\label{sec:perfproblems}

@@

\subsection{Problems of shared understanding}\label{sec:semproblems}

@@

\subsection{Problems with evaluations}\label{sec:evalproblems}

@@

\subsection{Development problems}\label{sec:devproblems}

@@

\subsection{Problems addressed by this work}\label{sec:probaddress}

@@

\subsection{Future work; Discussion of other problems}

>>>>

\subsection{Performance and Stability Problems}\label{sec:perfproblems}

@@

\subsection{Problems of Shared Understanding}\label{sec:semproblems}

@@

\subsection{Problems With Evaluations}\label{sec:evalproblems}

@@

\subsection{Development Problems}\label{sec:devproblems}

@@

\subsection{Problems Addressed by This Work}\label{sec:probaddress}

@@

\subsection[Future Work]{Future work; Discussion of Other Problems}

### 2016-06-21 dissertation/related.tex
typo #10
Capitalisation; thanks Helen

\section{Related work}\label{sec:related}

@@

\subsection{Query answering with cache}\label{sec:relcache}

@@

As such, this mirrors an extensive development known as ``Semantic
Caching'' in the database community. Ahmad et al. \cite{4777801}
surveyed the state of the art in that area. They divided caching
approaches into \emph{page}, \emph{tuple} and \emph{semantic} caches,
and noted that in the two former cases, if only partial results were
available in the cache, the entire result would have to be fetched
from the remote database. Indeed, a page or tuple cache may be used to
cache the results of a whole SPARQL query in HTTP context, but SPARQL
queries are also trivial to partition by e.g. triple patterns or Basic
Graph Patterns, which provides further opportunities for caching where
only partial results are available.\todo{Have I understood this
  correctly? See \url{http://ieeexplore.ieee.org/xpls/icp.jsp?arnumber=1161590#fig1}}

@@

HERMES \cite{adali1996query} provided motivation for
\ref{sec:conpush}, but is also important prior art for the work in
Chapter~\ref{sec:tpfcacheplanning}. An important concept in the HERMES
system is ``invariants''. They are, in our terminology, patterns that
do not need to be looked up remotely, but can be integrated in the
query answer by the mediator. The expectation in HERMES is that such
invariants will be encoded by a domain expert. The Attean framework,
which is used extensively in this work and is detailed in Section~\ref{sec:attean}
provides facilities to do this in an easy and extensible way, and also
accommodates for the task of computing a scalar cost metric, but
HERMES has a more advanced cost model in that it has a cost vector
with estimates for time required to find the first answer, time to
find all answers and the cardinality of the answer set. Caching
summary statistics is another important feature of HERMES, and it also
contributes lossy and lossless summaries, for the purpose of saving
space and reduce the time it takes to compute a cost estimate. HERMES
further has a query rewriter and optimiser, that rewrites the query
taking into account the cache and the invariants. While HERMES is more
general than what I detail in Chapter~\ref{sec:tpfcacheplanning}, we
note that while invariants could be coded in Attean, a SPARQL query
cache should be oblivious to domain knowledge and therefore shouldn't
assume any invariants, except in the possible but unlikely case where
the remote server declares that an infinite freshness lifetime for the
result of a certain graph pattern. While statistics summarisation is
relevant and should be studied in future work, we note that with a
Linked Data Fragments server, a cardinality estimate is required to be
available for every triple pattern, and is also cacheable with the
same constraints as the data themselves.

@@

Acosta et al. has published a poster on ``SHEPHERD''
\cite{acosta2014shepherd}, presumed to be have ongoing, to
create a SPARQL processor that takes into account observations done by
the SPARQLES survey \cite{buil2013sparql}, to decompose a SPARQL query into
subqueries that is indicated to be easier for the server to evaluate,
and so is well aligned with our goal to ease the load of the
server. It is not quite clear from the brief description in 
\cite{acosta2014shepherd} whether the SHEPHERD system can cache results locally.

>>>>

\section{Related Work}\label{sec:related}

@@

\subsection{Query Answering With Cache}\label{sec:relcache}

@@

As such, this mirrors an extensive development known as ``Semantic
Caching'' in the database community. Ahmad et al. \cite{4777801}
surveyed the state of the art in that area. They divided caching
approaches into \emph{page}, \emph{tuple} and \emph{semantic} caches,
and noted that in the two former cases, if only partial results were
available in the cache, the entire result would have to be fetched
from the remote database. Indeed, a page or tuple cache may be used to
cache the results of a whole SPARQL query in HTTP context, but SPARQL
queries are also trivial to partition by e.g. triple patterns or Basic
Graph Patterns, which provides further opportunities for caching where
only partial results are available.\todo{Have I understood this
  correctly? See \url{http://ieeexplore.ieee.org/xpls/icp.jsp?arnumber=1161590\#fig1}}

@@

HERMES \cite{adali1996query} provided motivation for the paper in
Section~\ref{sec:conpush}, but is also important prior art for the
work in Chapter~\ref{sec:tpfcacheplanning}. An important concept in
the HERMES system is ``invariants''. They are, in our terminology,
patterns that do not need to be looked up remotely, but can be
integrated in the query answer by the mediator. The expectation in
HERMES is that such invariants will be encoded by a domain expert. The
Attean framework, which is used extensively in this work and is
detailed in Section~\ref{sec:attean} provides facilities to do this in
an easy and extensible way, and also accommodates for the task of
computing a scalar cost metric, but HERMES has a more advanced cost
model in that it has a cost vector with estimates for time required to
find the first answer, time to find all answers and the cardinality of
the answer set. Caching summary statistics is another important
feature of HERMES, and it also contributes lossy and lossless
summaries, for the purpose of saving space and reduce the time it
takes to compute a cost estimate. HERMES further has a query rewriter
and optimiser, that rewrites the query taking into account the cache
and the invariants. While HERMES is more general than what I detail in
Chapter~\ref{sec:tpfcacheplanning}, we note that while invariants
could be coded in Attean, a SPARQL query cache should be oblivious to
domain knowledge and therefore shouldn't assume any invariants, except
in the possible but unlikely case where the remote server declares
that an infinite freshness lifetime for the result of a certain graph
pattern. While statistics summarisation is relevant and should be
studied in future work, we note that with a Linked Data Fragments
server, a cardinality estimate is required to be available for every
triple pattern, and is also cacheable with the same constraints as the
data themselves.

@@

Acosta et al. has published a poster on ``SHEPHERD''
\cite{acosta2014shepherd}, presumed to be ongoing work, to
create a SPARQL processor that takes into account observations done by
the SPARQLES survey \cite{buil2013sparql}, to decompose a SPARQL query into
subqueries that is indicated to be easier for the server to evaluate,
and so is well aligned with our goal to ease the load of the
server. It is not quite clear from the brief description in 
\cite{acosta2014shepherd} whether the SHEPHERD system can cache results locally.
